Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-06-02 outputs/paper/paper.qmd
Updating code to graph results

#code referenced from: https://github.com/christina-wei/INF3104-1-Covid-Clinics/blob/main/outputs/paper/covid_clinics.qmd
summarized_voter_statistics |>
  ggplot(aes(x = ward), "-", sub, fill = n) + 
  geom_bar() + #bar graph
  theme_minimal() + #neater theme
  theme(axis.text.x = element_text(angle=90, size = 6)) + #rotate x-axis & smaller font
  labs(
    title = "Number of Subdivisions Per Ward in Toronto",
    x = "Ward",
    y = "Number of Subdivisions",
    fill = "Type"
  )  #a

@@

head (cleaned_voter_statistics, 60) |>
 select(ward, sub) |>
  arrange (ward) |>
   kable(
    col.names = c("Ward", "Sub"),
  booktabs = TRUE
  )

>>>>

summarized_voter_statistics |>
  ggplot(mapping = aes(x = ward, y = n)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Number of Subdivisions per Ward",
    x = "Ward",
    y = "Number of Subdivisions",
  ) +
  theme_classic() +
  scale_fill_brewer(palette = "Set1")

@@

head (summarized_voter_statistics, 60) |>
   kable(
    col.names = c("Ward", "Sub"),
  booktabs = TRUE
  )
